A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-02-23 manuscript.tex
:construction: feature extraction link to appB

It is important to reiterate that the six selected time-series features are in no way exhaustive or imperative. Both using a more data-driven approach to features or selecting other aspects to summarize the time series are legitimate options \citep[e.g., see][]{heylen2016}. The list seeks to offer a practical toolbox of features that are common and meaningful to psychological research questions and -practice but are also easy to extract and summarize a broad range of developments without asserting strict assumptions (see \tblref{tab:esmFeatures} for an overview).

>>>>

It is important to reiterate that the six selected time-series features are in no way exhaustive or imperative. Both using a more data-driven approach to features or selecting other aspects to summarize the time series are legitimate options \citep[e.g., see][]{heylen2016}. The list seeks to offer a practical toolbox of features that are common and meaningful to psychological research questions and -practice but are also easy to extract and summarize a broad range of developments without asserting strict assumptions (see \tblref{tab:esmFeatures} for an overview and \appref{app:FeatureBackground} for additional information on the theoretical relevance of the selected features).
